---
title: "kickstarter EDA"
output: html_document
---

Questions to Answer:
How long does it take, on average, to obtain the goal amount of funding? 
How much, on average, does the amount of funding differ from goal?

Follow Up Questions:
Time elapsed between launch date and goal reached: 5 number summary and other important features --> look at distribution of days of successful campaigns

Mean/median time elapsed by top categories

Likelihood of success given days passed: Is there a point where ppl should just give up bc it’s been too long?  

1.
Found time elapsed (in days) between the day launched and the deadline, then subsetted data to only include successful (state = successful) campaigns.

```{r}
library(ggplot2)
ks <- read.csv("ks18.csv")
ks$deadline <- as.Date(ks$deadline)
ks$launched <- as.Date(ks$launched)
ks$timeElapsed <- (ks$deadline - ks$launched)
success <- subset(ks, ks$state == 'successful')

```
Summary of time elapsed of all campaigns:
```{r}
fivenum(ks$timeElapsed)

```
Summary of time elapsed of successful campaigns (and mean):
```{r}
fivenum(success$timeElapsed)
mean(success$timeElapsed)
```

The maximum time elapsed of a successful campaign was 92 days. 

2. Summary of funding difference of all campagins:

```{r}
ks$diff <- as.numeric(ks$usd.pledged) - as.numeric(ks$goal)
diffNAdrop <- ks$diff[complete.cases(ks$diff)]
fivenum(diffNAdrop)
mean(diffNAdrop)
```

Summary of funding difference of successful campaigns:
```{r}
success$diff <- as.numeric(success$usd.pledged) - as.numeric(success$goal)
successdiffNAdrop <- success$diff[complete.cases(success$diff)]
fivenum(successdiffNAdrop)
mean(successdiffNAdrop)
```

Visualizations:
Goal amount over Time Elapsed (Successful Campaigns)
```{r}
plot(success$timeElapsed, success$goal, 'h')

success$time_in_days <- as.numeric(success$timeElapsed)
ggplot(success, aes(time_in_days, goal)) + geom_point()
ggplot(success, aes(time_in_days, goal)) + geom_smooth()

ggplot(success, aes(time_in_days, goal)) + geom_point() + geom_smooth()

```

Campaigns that are successful are typically completed within 3 months, despite goal price.

Most likely day to be successful:

```{r}
getmode <- function(v) {
uniqv <- unique(v)
uniqv[which.max(tabulate(match(v, uniqv)))]
}
v<- success$time_in_days
getmode(v)
```

Top category and median time elapsed (success)

```{r}
getmode(ks$category)
x <- success$timeElapsed[which(success$category == "Product Design")]
median(x)

```
Top main category:
```{r}
getmode(ks$main_category)
y <- success$timeElapsed[which(success$main_category == "Film & Video")]
median(y)
```

